Quality assurance of digital twins -- An experience report in the automotive industry

### 2022-12-14 manuscripts/paper-1/main.tex
Last one before meeting

    The first occurrence of the "Digital Twin" term was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving the Product Lifecycle Management (PLM) course.~\cite{DTGRIEVES}
    His introduction to the term was rather raw but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" idea.

@@

    A virtual entity exists only in the virtual space, which should imitate the physical entity with high-fidelity models. If we consider the virtual entity as a function;

@@

    The last dimension is the connection between physical space and virtual space. Physical space created real-time data, and through the connection, these data will be received by the virtual space 
    and updates the states of the models. Virtual space sends the needed information to the physical space.

    There is also another, an up-to-date approach that adds two more dimensions(Data and Services), to the traditional digital twin model which is described above.~\cite{DTGRIEVES}

@@

    \begin{description}
        \item[PE] Represents DT Physical Entity
        \item[VE] Represents DT Virtual Entity
        \item[Ss] Represents DT Services
        \item[DD] Represents DT Data
        \item[CN] Represents DT Connections
    \end{description}
    If we consider the dimensions we above discussed as vertical dimensions, if we divide our digital twin horizontally into three different layers, the explanation of the digital twin systems becomes much clearer.
    \begin{itemize}
        \item Unit DT which only has one PE in the physical space
        \item System DT  is an assembly of PE's in the physical space
        \item System of Systems DT  is an assembly of systems in the physical space
    \end{itemize}

    Of course, there are other explanations, approaches, and architectures to digital twins, but like every other digital transformation approach, the main goal is to get into the lean state,
    which is an optimal approach to our problem.

    Also should be noted that the digital twin approach was introduced within the PLM course. PLM is nothing but an improvement to the lean manufacturing philosophy, which aims to eliminate waste(Time, energy, Material) not only during the
    manufacturing process but also during the lifecycle of the product.~\cite{grieves2006PLM} 
    It's an approach to achieve the lean state, which overlaps with the idea of digital twins, which both aim to gather more information about the product, starting from the design phase to the disposal of the product.

    Achieving a full-scale cyber-physical system is not only a goal for the digital twin but also an essential challenge. The following are some examples of the challenges which is occurring during the development of a digital twin:
    \begin{itemize}
        \item High fidelity modeling and simulation
        \item Real-Time communication between the components of digital twin 
        \item Flexible data architecture
        \item Developing standards and protocols for the use of digital twins so that they can be used consistently across different industries and applications.
        \item Cost and Cost Management
        \item Cyber Security
        \item Quality Assurance of the digital twin
        \item Information inefficiency regarding the theme Digital Twins
        \item \dots{}
    \end{itemize}

@@

    Methodology (see Section~\ref{section:liteature_methodology}), result (see Section~\ref{section:liteature_result}), and summary (See Section~\ref{section:liteature_summary})...
    \subsection{Methodology}~\label{section:liteature_methodology}
    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
    Since there is a great number of digital twin publications in academics, 
    narrowing the research is necessary, so the following algorithm which can be seen in Figure \ref{fig:literaturesearchalgorithm} with several levels of filtering will be applied.

    First filtering will be done with the following criteria:
    \begin{itemize}
        \item Dissertations should be written in English and published in a journal/conference.
        \item Paper is not older than 2018
        \item Search term should be exactly searched.
    \end{itemize}

@@

    Second filtering will be done to eliminate the duplications, which can occur when GS and SCP give the same result.
    \begin{itemize}
        \item Remove Duplications
        \item Remove the dissertations which are not English manually
    \end{itemize}

    Even though we already filtered the language, still some dissertations results will appear because of the auto translation which they put on the website.
    So second time should be filtered manually.

    After the second filtration, the third filtering which is a manual investigation should occur with the following filtering criteria:
    \begin{itemize}
        \item Proper literature review should be present in the selected paper
        \item Abstract and conclusion should be relevant to the search term
    \end{itemize}

    \begin{figure}
        \centering
        \includegraphics[width =0.45\textwidth]{LRMethod.png}
        \caption{Literature Search Algorithm}
        \label{fig:literaturesearchalgorithm}
    \end{figure} 
    \begin{figure}
        \centering
        \includegraphics[width =0.45\textwidth]{LRMethodLegacy.png}
        \caption{Literature Search Algorithm Legend}
        \label{fig:literaturesearchalgorithmlegend}
    \end{figure}

    %TODO: ADD THE METHOD HERE

    \subsection{Result}~\label{section:liteature_result}
    The following results were achieved by selecting several  search terms, which is 
    \subsubsection*{Digital Twin Quality}\label{subsection:Digital Twin Quality}

    First filtering is done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
    After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
    After the third filtering process, 9 dissertations passed and the rest is rejected.

    \subsubsection*{Digital Twin Testing}\label{subsection:Digital Twin Quality}
    %What is the existing literature?

@@

    What do we learn from existing literature?
    (Existing literature does at most partially solve our problem!)

>>>>

    The first occurrence of the "Digital Twin" term was introduced by Dr.~Michael Grieves in 2003 at the University of Michigan while giving the Product Lifecycle Management (PLM) course.~\cite{DTGRIEVES}
    His introduction to the term was rather raw but still introduced a pragmatic solution to gather more data from the physical entities, to achieve the "Lean" state.

@@

    On the other hand, a virtual entity exists only in the virtual space, which should imitate the physical entity with high-fidelity models. If we consider the virtual entity as a function;

@@

    The last dimension of a 3D-DT is the connection between physical space and virtual space. Physical space creates real-time data, and through the connection, these data will be received by the virtual space 
    and updates the states of the models. Virtual space sends the needed information to the physical space.

    There is also another, an up-to-date approach that adds two more dimensions (Data and Services), to the traditional digital twin model which is described above.~\cite{DTGRIEVES}

@@

    \begin{description}
        \item[PE] Represents DT Physical Entity
        \item[VE] Represents DT Virtual Entity
        \item[Ss] Represents DT Services
        \item[DD] Represents DT Data
        \item[CN] Represents DT Connections
    \end{description}
    If we consider the dimensions, we discussed above as vertical dimensions within a single layer, the digital twins also can have three different horizontal layers\cite{TAOCHAPTER1}. 
    The need for such layers is that the explanation of the digital twin systems becomes much clearer. These can be identified as:
    \begin{itemize}
        \item Unit DT has one PE in the physical space
        \item System DT is an assembly of PE's in the physical space
        \item System of Systems DT is an assembly of systems in the physical space
    \end{itemize}

    There is also the possibility to add more horizontal layers and define them differently such as a Part layer, Component layer, Machine layer, Production line layer, Shop-floor Layer.\cite{MultiScaleModeling4Layers}

    Of course, there are other explanations, approaches, and architectures to digital twins, but like every other digital transformation approach, the main goal is to get into the lean state,
    which regards the optimal approach to any problem.

    Also should be noted that the digital twin approach was introduced within the PLM course. PLM is nothing but an improvement to the lean manufacturing philosophy,
    which aims to eliminate waste (Time, Energy and Material waste) not only during the
    manufacturing process but also during the lifecycle of the product.~\cite{grieves2006PLM} 
    It's an approach to achieve the lean state, which overlaps with the idea of digital twins. Both aim to gather more information about the product, starting from the design phase to the disposal of the product.

    Achieving a full-scale cyber-physical system is not only a goal for the digital twin but also an essential challenge. The following are some examples of the challenges which is occurring during the development of a digital twin:
    \begin{itemize}
        \item High fidelity modeling and simulation
        \item Real-Time communication between the components of digital twin 
        \item Flexible data architecture
        \item Developing standards and protocols for the use of digital twins so that they can be used consistently across different 
        industries and applications
        \item Cost and Cost Management
        \item Cyber Security
        \item Quality Assurance of the digital twin
        \item Information inefficiency
        \item \dots{}
    \end{itemize}

@@

    Methodology (see Section~\ref{section:liteature_methodology}), Result (see Section~\ref{section:liteature_result}), and Summary (See Section~\ref{section:liteature_summary})...
    \subsection{Methodology}~\label{section:liteature_methodology}
    Google Scholar (GS), Scopus (SCP) and Research Rabbit (RR) tools are used to fulfill our requirements for the literature review. 
    Since there is a great number of digital twin publications in academics, 
    narrowing the research is necessary, so the following algorithm which can be seen in Figure \ref{fig:literaturesearchalgorithm} with several levels of filtering will be applied.

    First filtering will be done with the following criteria:
    \begin{itemize}
        \item Dissertations should be written in English and published in a journal/conference.
        \item Dissertations should not be older than 2018
        \item Search term should be exactly searched.
    \end{itemize}

@@

    Second filtering will be done to eliminate the duplications and even though authors already filtered the search for the English language,
    still some results without the English language will appear. Again, language filtering should be done to clean the results.

    \begin{itemize}
        \item Remove Duplications
        \item Remove the dissertations which are not English manually
    \end{itemize}

    After the second filtration, the third filtering which is a manual investigation should occur with the following filtering criteria:
    \begin{itemize}
        \item Proper literature review should be present in the selected dissertation
        \item Abstract and conclusion should be relevant to the search term
    \end{itemize}

    If an interesting dissertation(s) would be found during the reading, it will be checked again with the first filter.
    \begin{figure}
        \centering
        \includegraphics[width =0.45\textwidth]{LRMethod.png}
        \caption{Literature Search Algorithm}
        \label{fig:literaturesearchalgorithm}
    \end{figure} 
    \begin{figure}
        \centering
        \includegraphics[width =0.45\textwidth]{LRMethodLegacy.png}
        \caption{Literature Search Algorithm Legend}
        \label{fig:literaturesearchalgorithmlegend}
    \end{figure}

    \subsection{Result}~\label{section:liteature_result}
    The following results were achieved by selecting several search terms.
    \subsubsection*{Digital Twin Quality}\label{subsection:DigitalTwinQuality}

    First filtering was done for the search term "digital twin quality", meanwhile GS gave 41 different results, and SCP gave only 3 results.
    After the second filtering process, 3 duplications and 31 different results were found. 10 dissertations were not in English.
    After the third filtering process, 9 dissertations passed and the rest is rejected.

    \subsubsection*{Digital Twin Model Verification}\label{subsection:DigitalTwinVerification}

    \subsubsection*{Digital Twin Model Validation}\label{subsection:DigitalTwinValidation}
    %What is the existing literature?

@@

    What do we learn from existing literature?

    He Zhang et al.introduced a consistency evaluation method for digital twin models, which can be used to assess the quality of the digital twin~\cite{ConsistencyEvolutionMethodForDigitalTwins}.
    (Existing literature does at most partially solve our problem!)
